Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-05-27 submission/Sze_Obesity_PeerJ_2016.Rmd

**Figure 3: Meta Analysis of the Relative Risk of Obesity Based on Shannon Diversity or Bacteroidetes/Firmicutes Ratio.**  Groups were divided for each study on high and low Shannon Diversity or Bacteroidetes/Firmicutes (B/F) ratio groups based on the median for that study. Red represents studies that used the 16S rRNA V4 region, yellow represents studies that used a V1-V3 approach, blue represents studies that used either a V1-V2 or just a V2 approach, and orange represents studies that used the V3-V5 region.  **A)** The overall pooled relative risk for Shannon Diversity was `r format(round(RR_composite['shannon', 'rr'],2), nsmall=2)` with a P-value of `r format(round(RR_composite['shannon', 'p_value']), nsmall=2)`.  **B)** The overall pooled relative risk for the B/F ratio was  `r format(round(RR_composite['bf_ratio', 'rr'],2), nsmall=2)` with a P-value of `r format(round(RR_composite['bf_ratio', 'p_value'], 2), nsmall=2)`.

>>>>

**Figure 3: Meta Analysis of the Relative Risk of Obesity Based on Shannon Diversity or Bacteroidetes/Firmicutes Ratio.**  Groups were divided for each study on high and low Shannon Diversity or Bacteroidetes/Firmicutes (B/F) ratio groups based on the median for that study. Red represents studies that used the 16S rRNA V4 region, yellow represents studies that used a V1-V3 approach, blue represents studies that used either a V1-V2 or just a V2 approach, green represents studies that used a V3-V4 region, and orange represents studies that used the V3-V5 region.  **A)** The overall pooled relative risk for Shannon Diversity was `r format(round(RR_composite['shannon', 'rr'],2), nsmall=2)` with a P-value of `r format(round(RR_composite['shannon', 'p_value']), nsmall=2)`.  **B)** The overall pooled relative risk for the B/F ratio was  `r format(round(RR_composite['bf_ratio', 'rr'],2), nsmall=2)` with a P-value of `r format(round(RR_composite['bf_ratio', 'p_value'], 2), nsmall=2)`.
